MLH1 data report 

### 2017-11-16 rmd_report.rmd
trying to debg report.rmd
fixed the rmd file

```{r, histogram, echo=FALSE, fig.caption= "histograms", warning=FALSE, fig.align='center'}

histM <- ggplot(MLH1_data,(aes(adj_nMLH1.foci))) + xlim(c(16, 38))
histM <- histM + geom_histogram(stat = "bin", binwidth = 1)
histM <- histM + facet_wrap(~ category)
histM
```

@@

latice plot of scatter plots for jitter plots of cell oberservations by quality. The category mean is in black and the mouse specific mean is in red.
```{r, echo=FALSE, message=FALSE,results='hide', warning=FALSE}
#what is the purpose of this block
df_list <- split(MLH1_data, (MLH1_data$category))
#remove sections which are in category but have no data
df_list <- df_list[ -c(7, 12, 14,16, 18) ]
#7, PERC. 12 CASTF, 14 HMI f , 16 SPRET f. 18 other

>>>>

```{r, histogram, echo=FALSE, fig.caption= "histograms", warning=FALSE, fig.align='center'}
#consider making distribution with quality considered...
histM <- ggplot(MLH1_data,(aes(adj_nMLH1.foci))) + xlim(c(16, 38))
histM <- histM + geom_histogram(stat = "bin", binwidth = 1)
histM <- histM + facet_wrap(~ category)
histM
```

@@

latice plot of scatter plots for jitter plots of cell oberservations by quality. The category mean is in black and the mouse specific mean is in red.
```{r, echo=FALSE, message=FALSE,results='hide', warning=FALSE}
#what is the purpose of this block
df_list <- split(MLH1_data, (MLH1_data$category))
#remove sections which are in category but have no data
df_list <- df_list[ -c(7, 12, 14,19, 20) ]
#7: PERC male, 12:CAST female, 14:HMI female, 19:SPIC male
